Supplement to Global Distribution of Unintended Pregnancies and Contraceptive Usage Project

### 2024-03-15 products/manuscript/supplement/Supplementary-Material.qmd
Final Part 3 Updates
I organized the eda file and added some final interpretations. I cleaned the manuscript file to only include relevant information in the correct order and made sure the document renders.

This shows some materials that could go into a supplementary file. Often you want/need references here too. You can use the same reference bib file for this and the main text (as done here) or have separate bib files.

@@

Of course you would choose the format based on needs.

I'm also using a different style for the references here. (vancouver vs apa in the main manuscript). Usually one would have the formatting of the references the same in those two documents, but I want to illustrate how easy it is to switch reference formatting styles, you just need to get the right CSL file and specify it in the YAML header. We could also have a seperate reference bibtext (`.bib`) file, but here we are using the same.

# Overview

Readers will be able to find our analysis of the different contraception methods through figures we've made for the `pct_upreg_larcster`, `pct_upreg_trad`, and `pct_upreg_nouse` variables.

@@

```
Plot 10 shows `pct_upreg_larcster` vs `larcster_standard` to analyze women using long acting reversible methods and sterilization versus the percentage of unintended pregnancies using those methods.

@@

## Example additional result

>>>>

@@

# Overview
This file provides extra information that is not included in our manuscript or the main processing and exploratory data analysis files. This information provides guidance on our thought processes behind the scenes and explains why we chose a single outcome to study.

Readers will be able to find our analysis of the different contraception methods that we did not select for our main outcome through figures we've made for the `pct_upreg_larcster`, `pct_upreg_trad`, and `pct_upreg_nouse` variables.

@@

Plot 10 shows `pct_upreg_larcster` vs `larcster_standard` to analyze women using long acting reversible methods and sterilization versus the percentage of unintended pregnancies using those methods.

@@

## Additional result
The first priority when cleaning the data was analyzing missing values, and our findings can be seen @tbl-summarytable. We found that the `pct_upreg` variable containing the percentage of unintended pregnancies is unreliable due to missing data that could not be explained. We decided to use the variables with percentage of unintended pregnancies related to each birth control method as our outcome variables because they are complete and were found directly based on the AIU protocol information. We printed the summary table here because it was useful in determining missingness and creating a new factor variable for the usage of each birth control method at the factor level later in the processing sequence. 
```{r}
#| label: tbl-summarytable1
#| tbl-cap: "Summary table to discover missingness"
#| echo: FALSE
resulttable1 <- readRDS("../../results/tables/summarytable.rds")
kable(resulttable1)
```

We explored the distribution of the countries by five categorical variables: `region`, `larcster_usage`, `sarc_usage`, `trad_usage`, and `none_usage` which is displayed in @tbl-summarytable2. We found that most countries are located in Africa followed by Asia and Latin America/the Caribbean. Only 20 countries have high usage of long acting reversible and sterilization methods compared to 33 countries with high usage of short acting reversible and traditional methods. It is interesting that the distributions for short acting reversible method, traditional method, and no method usages are the same. 
```{r}
#| label: tbl-summarytable2
#| tbl-cap: "Summary table for categorical variables"
#| echo: FALSE
resulttable2 <- readRDS("../../results/tables/summarytablecat.rds")
kable(resulttable2)
```
